The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-11 paper.tex
New paper.tex from Kirill

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
  \caption[]{Left, center: images $Q1$ and $Q2$ used in the demostration of
    approximation for $1 / \sin \phi$. Right: Interfaces between phases are
    line segments which intersect each other at angle $\phi$. Shaded area is
    where $|(H*Q1\cdot(H*Q2)|$ has non-zero values. Sum of all values in this
    area approximates $1 / \sin \phi$.}
  \label{fig:experiment-setup}
\end{figure}
Consider two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
between black and white areas cross each other at the angle $\phi$. We apply an
edge detection filter to each image, multiply results element-wise and sum all
elements of the product. We want the resulting value to approximate
$1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
better than $H$. Why this is important will be explained in the next section.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary images on \cref{fig:experiment-setup}.}
  \label{fig:filter-comparison}
\end{figure}

@@

\section{Verification and computation results}
\label{sec:results}
In this section we consider a variety of examples of sets for which the developed
precise algorithm is applicable. We intercompare surface-surface functions
calculated with the algorithm for digital images (\cref{sec:algo}) with results
of the novel continuous algorithm. We also demostrate the work of both filter $H$ (\ref{eq:filter-3x3}) for edge
detection along with a new filter $H'$ (\ref{eq:filter-7x7}) proposed in this
paper. We verify both digital and continuous methods against available analytical solutions.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
  \caption[]{Left, center: images $Q_1$ and $Q_2$ used in the demostration of
    approximation for $1 / \sin \phi$. Right: Interfaces between phases are
    line segments which intersect each other at angle $\phi$. Shaded area is
    where $|(H*Q_1\cdot(H*Q_2)|$ has non-zero values. Sum of all values in this
    area approximates $1 / \sin \phi$.}
  \label{fig:experiment-setup}
\end{figure}
Consider two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
between black and white areas cross each other at the angle $\phi$. We apply an
edge detection filter to each image, multiply results element-wise and sum all
elements of the product. We want the resulting value to approximate
$1/\sin \phi$. As can be seen on \cref{fig:filter-comparison} $H'$ does this job
better than $H$. Why this is important will be explained in the next section.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/filter-comparison.png}
  \caption[]{Estimation of $1/\sin\phi$ by filters $H$ and $H'$ for binary
    images on \cref{fig:experiment-setup}.}
  \label{fig:filter-comparison}
\end{figure}

@@

\section{Verification and computation results}
\label{sec:results}
In this section we consider a variety of examples of sets for which the developed
precise algorithm is applicable. We intercompare surface-surface functions
calculated with the algorithm for digital images (\cref{sec:algo}) with results
of the novel continuous algorithm. We also demonstrate the work of both filter
$H$ (\ref{eq:filter-3x3}) for edge detection along with a new filter $H'$
(\ref{eq:filter-7x7}) proposed in this paper. We verify both digital and
continuous methods against available analytical solutions.
